\plaintitle

### 2016-08-09 drafts/labor/cases.tex
debugging a bunch of unnecessary stuff to get biblatex working...

\subsection{What are the limits of crowdsourcing?}
For more than a decade
research in crowd work has explored ways of expanding the work that crowdsourcing can do by
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes,
and repeating the process
\cite[etc\dots]{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been whether there are limits to crowdsourcing
(and, if so, what bounds them).

@@

Work decomposition, then, is far from new;
``decomposition'' generally illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger and warned of it in
\citeyear{professionalCrowdworkEthics}
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in his documentary work
\citetitle{riisOtherSideLives}
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

@@

The effect low wages have had on piece work and factory workers is well--known;
\citeauthor{gantt1913work} discuss this exact mechanism in his book on
\citetitle{gantt1913work}, pointing out that
``\dots~where there is no union,
the class wage is practically gauged by the wages the poor workman will accept,
and the good workman soon becomes discouraged and \textit{sets his pace by that of his less efficient neighbor},
with the result that the general tone of the shop is lowered'' (emphasis added)
\cite{gantt1913work}.

@@

Resistance against managers in piecework and factory labor settings are deeply well--explored,
but perhaps the most relevant case study to draw on here is to be found in
\citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
\cite{waldinger1996helots}.
The achievements of labor advocacy groups such as labor unions as resistant,
even adversarial organizations counter--balancing the management
is somewhat well--understood
\cite{russell1982collective,craig1992behavior}.
We argue that these threads of resistance against management in various forms
are in fact one.
}
\end{document}

>>>>

\subsection{What are the limits of crowdsourcing?}
For more than a decade
research in crowd work has explored ways of expanding the work that crowdsourcing can do by
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes,
and repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been whether there are limits to crowdsourcing
(and, if so, what bounds them).

@@

Work decomposition, then, is far from new;
``decomposition'' generally illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger and warned of it in
\citeyear{professionalCrowdworkEthics}
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in his documentary work
% \citetitle{riisOtherSideLives}
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

@@

The effect low wages have had on piece work and factory workers is well--known;
\citeauthor{gantt1913work} discuss this exact mechanism in his book on
% \citetitle{gantt1913work}, pointing out that
``\dots~where there is no union,
the class wage is practically gauged by the wages the poor workman will accept,
and the good workman soon becomes discouraged and \textit{sets his pace by that of his less efficient neighbor},
with the result that the general tone of the shop is lowered'' (emphasis added)
\cite{gantt1913work}.

@@

Resistance against managers in piecework and factory labor settings are deeply well--explored,
but perhaps the most relevant case study to draw on here is to be found in
\citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
\cite{waldinger1996helots}.
The achievements of labor advocacy groups such as labor unions as resistant,
even adversarial organizations counter--balancing the management
is somewhat well--understood
\cite{russell1982collective,craig1992behavior}.
We argue that these threads of resistance against management in various forms
are in fact one.
}

\onlyinsubfile{
  \balance{}
  \printbibliography
}

\end{document}

### 2016-08-09 drafts/labor/trackingWork.tex
debugging a bunch of unnecessary stuff to get biblatex working...

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth}
\usepackage[normalem]{ulem}
% \usepackage[citestyle=numeric,backend=bibtex,bibencoding=ascii]{biblatex}
\usepackage{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdftex,pdfpagelabels=false]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{references}

@@

\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions \cite{}
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.

@@

For insight on this, we return to \citeauthor{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
% Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% unable to satisfy their needs or otherwise more invested in the 
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

% \bibliographystyle{SIGCHI-Reference-Format}

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{references}
% \addbibresource{references}

@@

\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.

@@

For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% unable to satisfy their needs or otherwise more invested in the 
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.
